Waving and swaying

### 2014-08-28 Paper/grass.tex
figure recovery

\graphicspath{ {images/}{images/Growth_Rate_Cont_Plots/} }
\newcommand{\ellcap}{{\ell_\text{c}}}
\newcommand{\Fh}{{\boldsymbol{F}_h}}
\newcommand{\Fv}{{\boldsymbol{F}_v}}
\newcommand{\Tv}{{\boldsymbol{T}}}
\newcommand{\bn}{{\boldsymbol{n}}}
\newcommand{\bt}{{\boldsymbol{t}}}
\newcommand{\bz}{{\boldsymbol{z}}}
\newcommand{\bx}{{\boldsymbol{x}}}
\newcommand{\by}{{\boldsymbol{y}}}
\newcommand{\bT}{{\boldsymbol{T}}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\grad}{\mathbf{\nabla}}
\newcommand{\del}{\partial}

@@

continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$ in the fluid momentum balance\cite{Vivoni98,Nepf99,Ghisal02,Delangre04,Delangre06} 
\shreyas{Where did this model come from? Has such a model been used before? Citations to those needed.} as

@@

vary with distance from the bottom but we do not expect these variation to be central to the mechanism and therefore take $C_N$ \& $N_g$ to be constants.

@@

The steady uniform flow $U(y)$ resulting from solution of \eqref{navier-stokes} is expected to be unstable, leading to coherent eddies underlying monami. Steady state flow driven by   
%We perform linear stability analysis of a base state associated with the vegetated flow to gain insight about instability characteristics of flow in presence of grass.
constant pressure gradient satisfies
$-{dP}/{dx}+\mu U''(y) +S(y) \rho C_N d N_gU^2=0$, where $S(y)=1$ in the vegetated layer $0<y<h_{grass}$ and $S(y)=0$ in the unvegetated layer $h_{grass}< y< H$. 

@@

give rise to a boundary layer in the flow profile near the tip of the grass. The boundary layer near the canopy top may be identified 
as a free shear layer\cite{Ghisal02} in the previous explanation of monami and its dependence on the grass density $N_g$ gives us a direct control of its thickness. 
In our model, the thickness of shear layer near top of grass is obtained by balance of viscous force 
with drag along with matching shear at grass tip exerted by flow in unvegetated region, which leads to shear layer 
thickness $\delta \sim  H\left[({\rho U_0 H}/\mu) (C_N d N_g H)\right]^{-1/3}$\normalsize where \small$U_0 = \frac{dP/dxH^2}{\mu}$\normalsize is scale for velocity and
$H$ is half channel width.

@@

Knowing the scale of shear layer we can systematically investigate its effect on flow instability
by varying grass number density $N_g$ and pressure gradient $\frac{dP}{dx}$. Considering small perturbations $u, v, p$ about the base profile $U$ and $P$
respectively, momentum and mass balance equation expanded in first order of perturbed variable yields

@@

We are left with three non-dimensional parameters in the model, viz. the Reynolds number $R= {\rho U_0 H}/{\mu}$, the drag parameter $\delta/H$, 
and the submergence ratio of the grass $h_g/H$. With these scaling along with the use of stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance; 

@@

Seeking wave solution in form of $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma t}$,  
we get modified Orr-Sommerfield equation. The eigenvalue $\sigma$ for a given $k$ provides growth rate and frequency associated with a perturbation of wavelength $2\pi/k$.

@@

@@

\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens28_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens30_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens32_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set4_dens34_imgsc}}

\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens38_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens40_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens42_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set5_dens46_imgsc}}

\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens32_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens34_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens36_imgsc}}
\subfigure[]{\includegraphics[scale = 0.55]{Set6_dens38_imgsc}}

>>>>

\graphicspath{ {images/}{images/Growth_Rate_Cont_Plots/} }
\newcommand{\ellcap}{{\ell_\text{c}}}
\newcommand{\Fh}{{\boldsymbol{F}_h}}
\newcommand{\Fv}{{\boldsymbol{F}_v}}
\newcommand{\Tv}{{\boldsymbol{T}}}
\newcommand{\bn}{{\boldsymbol{n}}}
\newcommand{\bt}{{\boldsymbol{t}}}
\newcommand{\bz}{{\boldsymbol{z}}}
\newcommand{\bx}{{\boldsymbol{x}}}
\newcommand{\by}{{\boldsymbol{y}}}
\newcommand{\bT}{{\boldsymbol{T}}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\grad}{\mathbf{\nabla}}
\newcommand{\del}{\partial}
\newcommand{\hg}{h_g}

@@

continuous body force $\mathbf{f}=-N_g\mathbf{f_d}$ in the fluid momentum balance\cite{Vivoni98,Nepf99,Ghisal02,Delangre04,Delangre06} as

@@

vary with distance from the bottom but we do not expect these variation to be central to the mechanism and therefore take $C_N$ \& $N_g$ to be constants. Based on previous experiments\cite{Vivoni98}, we take $C_N \approx 1$.

@@

For consistency of analysis, we calculate the steady flow as a solution of \eqref{navier-stokes}, and examine its linear stability. The steady uniform flow $U(y)$ resulting from solution of \eqref{navier-stokes} is expected to be unstable, leading to coherent eddies underlying monami. Steady state flow driven by constant pressure gradient satisfies
$-{dP}/{dx}+\mu U''(y) +S(y) \rho C_N d N_gU^2=0$, where $S(y)=1$ in the vegetated layer $0<y<\hg$ and $S(y)=0$ in the unvegetated layer $\hg< y< H$. 

@@

give rise to a boundary layer in the flow profile near the tip of the grass. The boundary layer near the canopy top results from purely local dynamics independent of the influence of the boundaries, and may therefore be identified as a free shear layer\cite{Ghisal02} in the previous explanation of monami. 
In our model, this boundary layer thickness is obtained by balance of viscous force with drag, and matching the shear with that in unvegetated region. This leads to a shear layer 
thickness $\delta \sim  H\left[({\rho U_0 H}/\mu) (C_N d N_g H)\right]^{-1/3}$ where $U_0 = {(dP/dx)~H^2}/{\mu}$ is scale for velocity and
$H$ is half channel width. Its dependence on the grass density $N_g$ gives us a direct control of its thickness. 

@@

Knowing the scale of shear layer we can systematically investigate its effect on flow instability by varying grass number density $N_g$ and pressure gradient ${dP}/{dx}$. Considering small perturbations $u, v, p$ about the base profile $U$ and $P$ respectively, momentum and mass balance equation expanded in first order of perturbed variables yields

@@

We are left with three non-dimensional parameters in the model, viz. the Reynolds number $R= {\rho U_0 H}/{\mu}$, the vegetation drag parametrized as $\delta/H$, 
and the submergence ratio of the grass $h_g/H$. With these scaling, and using a stream function $\psi$ with $u = \psi_{y}, v= -\psi_x$ to satisfy mass balance, we seek a wave solution of the form $\left(u,v,\psi \right)= \left(\hat u, \hat v, \hat\phi \right)e^{ikx+\sigma t}$ to  obtain a modified Orr-Sommerfield equation. 

@@

The eigenvalue $\sigma$ for a given $k$ provides growth rate and frequency associated with a perturbation of wavelength $2\pi/k$ through the solution of

@@

\shreyas{Boundary conditions?}

@@

\subfigure[]{\includegraphics[scale = 0.72]{Set4_dens28_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set4_dens30_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set4_dens32_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set4_dens34_imgsc}}

\subfigure[]{\includegraphics[scale = 0.72]{Set5_dens38_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set5_dens40_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set5_dens42_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set5_dens46_imgsc}}

\subfigure[]{\includegraphics[scale = 0.72]{Set6_dens32_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set6_dens34_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set6_dens36_imgsc}}
\subfigure[]{\includegraphics[scale = 0.72]{Set6_dens38_imgsc}}
